Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-22 paper.qmd
Update link to run_polyglot_example.sh script

The complete, runnable source code for this example is available in the paper's GitHub repository. 
A shell script, `run_polyglot_example.sh`, is provided to automate the entire process from environment 
creation to final output, as described at the end of this section^[\url{https://github.com/b-rodrigues/rix_paper/blob/master/run_polyglot_example.sh}].

>>>>

The complete, runnable source code for this example is available in the paper's GitHub repository. 
A shell script, `run_polyglot_example.sh`, is provided to automate the entire process from environment 
creation to final output, as described at the end of this section^[\url{https://github.com/b-rodrigues/rix_paper/blob/master/polyglot-example/run_polyglot_example.sh}].
